$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-06 paper/paper.tex
Update subst theorem in the appendix
on benefits of leftovers

\todo{spellcheck}
\todo{make sure all citations are there}
\todo{lemmas in appendix are referred to from here}

@@

    \item \textbf{\picalc{} with leftovers}: Our type system uses \emph{leftover typing} to model the resource-aware \picalc{} (\autoref{leftover-typing}).
    This approach adds a leftover usage context to the typing judgements.
    Typing derivations take the resources of their input usage context, consume some of them, and leave the rest as leftovers in the output usage context.
    One of the benefits of this technique is that it removes the need for extrinsic context splits, which are rendered unnecessary.
  \end{itemize}
  \item \textbf{Machine verified proofs of subject reduction and auxiliary theorems}:
  \autoref{type-safety} details the type safety properties of our \picalc{} with leftovers.
  Leftover typing allows \emph{framing} (\autoref{thm:framing}), \emph{weakening} (\autoref{thm:weakening}) and \emph{strengthening} (\autoref{thm:strengthening}) theorems to be stated.
  We use these to prove \emph{subject congruence} (\autoref{subject-congruence}), and together with \emph{substitution} (\autoref{substitution}), to prove \emph{subject reduction} (\autoref{subject-reduction}).

>>>>

\todo{spellcheck}
\todo{make sure all citations are there}
\todo{lemmas in appendix are referred to from here}
\todo{shorten: we are slightly over the limit}

@@

    \item \textbf{\picalc{} with leftovers}: Our type system uses \emph{leftover typing} to model the resource-aware \picalc{} (\autoref{leftover-typing}).
    This approach adds a leftover usage context to the typing judgements.
    Typing derivations take the resources of their input usage context, consume some of them, and leave the rest as leftovers in the output usage context.

    Benefits of typing with leftovers include: removing the need for extrinsic context splits, which are rendered unnecessary; and for the first time we can state theorems like \textbf{weakening} (\autoref{thm:weakening}) and \textbf{strengthening} (\autoref{thm:strengthening}) in the linear \picalc{}.    
  \end{itemize}
  \item \textbf{Machine verified proofs of subject reduction and auxiliary theorems}:
  \autoref{type-safety} details the type safety properties of our \picalc{} with leftovers.
  Leftover typing allows \emph{framing} (\autoref{thm:framing}), \emph{weakening} (\autoref{thm:weakening}) and \emph{strengthening} (\autoref{thm:strengthening}) theorems to be stated.
  We use these to prove \emph{subject congruence} (\autoref{subject-congruence}), and together with \emph{substitution} (\autoref{substitution}), to prove \emph{subject reduction} (\autoref{subject-reduction}).
